Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-06 prop_letter.tex
prop_letter.tex \section{Results} Added...

@@

\newpage{}

In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum probability measure can be recast as an interval-valued
one. When $d\ge3$, the question reduces to Gleason's theorem which
states that for any quantum IVPM~$\bar{\mu}$, there is an unique
state consistent with $\bar{\mu}$ on every projector.

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
However, before diving into the Kochen-Specker theorem, it is better
to understand how to define the expectation value of an observable
with quantum IVPMs.

After we defined the expectation value, we will use the essential
idea of the Kochen-Specker theorem to prove there is no quantum IVPM
mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
then we have 
\begin{equation}
\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $.

However, even if a quantum IVPM approximates some states for each
classical sub-event space, it may not approximate any particular state
while considering all projectors~$\events$.

\begin{example}[Three-dimensional quantum three-interval-valued probability
measure\label{ex:three-dimensional-three-value}]
Given a three dimensional Hilbert space with an orthonormal basis
$\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
 & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}$ is a quantum IVPM.

@@

We found this kind of incompatibility can be reduced if we increase
the measurement resource, that is, using finer intervals. We conjecture
by consuming more and more measurement resource, it would be more
and more likely that a quantum IVPM has a state consistent with it
on all projectors~$\events$.

\yutsung{Although Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
it seems not directly relating to empty/non-empty core. On one hand,
the part using hidden variables cannot really apply on quantum IVPM
expect $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
case. On the other hand, for the part predicted by quantum mechanics,
the product of observables in inequalities are always either $\mathbb{1}$
or $-\mathbb{1}$ whose the interval-valued probabilities and expectation
values are always $\necess$. In this kind of situation, the inequalities
applies on all IVPMs, no matter whether it has an empty or non-empty
core.}

>>>>

\paragraph{Conventional Quantum Theory (\emph{CQT})}

@@

\section{Results}

In CQT, Gleason's theorem asserts any quantum real-valued probability
measure is consistent with a unique mixed state, and Shapley proved
a convex quantum IVPM must approximate some states for each classical
sub-event space. However, a quantum IVPM may not approximate any particular
state while considering all projectors~$\events$.

\begin{example}[Three-dimensional quantum three-interval-valued probability
measure\label{ex:three-dimensional-three-value}]
Given a three dimensional Hilbert space with an orthonormal basis
$\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
 & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}$ is a convex quantum
IVPM.

@@

Although Gleason's theorem doesn't hold for every quantum IVPM, when
the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum IVPM can be recast as an real-valued one. When $d\ge3$,
the question reduces to Gleason's theorem which states that for any
quantum IVPM~$\bar{\mu}$, there is an unique state consistent with
$\bar{\mu}$ on every projector. In general, this kind of inconsistency
can be reduced if we increase the measurement resource, that is, using
finer intervals. We conjecture by consuming more and more measurement
resource, it would be more and more likely that there is a state consistent
with a quantum IVPM on all projectors~$\events$.

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
We will use the essential idea of the Kochen-Specker theorem to prove
there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
then we have 
\begin{equation}
\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $.
